Predicting Political Support in the United States

### 2024-03-16 output/paper.qmd
split tables

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-cesdata
#| tbl-cap: "2022 CES (Cooperative Election Study) Data"

@@

ces2022_2 |>
  head() |>
  kable(
    col.names = c("Voted For (2020)", "Age Group", "Gender", "Education", "Race", "Religion", "Household Gun Ownership", "Student Loan Status"),
    booktabs = TRUE
  )
```

@@

# Appendix

>>>>

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-cesdata1
#| tbl-cap: "2022 CES (Cooperative Election Study) Data (Cultural)"

@@

ces2022_1 |>
  head() |>
  kable(
    col.names = c("Voted For (2020)", "Age Group", "Gender", "Education", "Race", "Religion"),
    booktabs = TRUE
  )
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-cesdata2
#| tbl-cap: "2022 CES (Cooperative Election Study) Data (Cultural) Standings"

ces2022_2 |>
  select(voted_for, household_gun_ownership, student_loan_status) |>
  head() |>
  kable(
    col.names = c("Voted For (2020)", "Household Gun Ownership", "Student Loan Status"),
    booktabs = TRUE
  )

@@

# Appendix {-}
